A pipeline to analyse time-course gene expression data

### 2020-04-29 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2019-11-19 02:22:00.

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0007224 & smoothened signaling pathway & 74 & 69 & 57.82 & 0.00041 & 0.326\\
GO:0010970 & transport along microtubule & 82 & 75 & 64.07 & 0.00045 & 0.326\\
GO:0048562 & embryonic organ morphogenesis & 155 & 137 & 121.10 & 0.00067 & 0.378\\
GO:0060173 & limb development & 92 & 84 & 71.88 & 0.00067 & 0.378\\
GO:0006805 & xenobiotic metabolic process & 47 & 45 & 36.72 & 0.00089 & 0.451\\
\addlinespace
GO:0060070 & canonical Wnt signaling pathway & 152 & 134 & 118.76 & 0.00099 & 0.456\\
GO:0019395 & fatty acid oxidation & 53 & 51 & 41.41 & 0.00133 & 0.562\\
GO:0055114 & oxidation-reduction process & 533 & 458 & 416.42 & 0.00152 & 0.593\\
GO:0090596 & sensory organ morphogenesis & 134 & 118 & 104.69 & 0.00216 & 0.783\\
GO:0010811 & positive regulation of cell-substrate ad... & 77 & 70 & 60.16 & 0.00260 & 0.879\\
\addlinespace
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.78 & 0.00293 & 0.929\\
GO:0021510 & spinal cord development & 48 & 45 & 37.50 & 0.00339 & 1.000\\
GO:0016571 & histone methylation & 74 & 67 & 57.82 & 0.00418 & 1.000\\
GO:0042738 & exogenous drug catabolic process & 22 & 22 & 17.19 & 0.00435 & 1.000\\
GO:1901381 & positive regulation of potassium ion tra... & 22 & 22 & 17.19 & 0.00435 & 1.000\\
\bottomrule
\end{tabular}

@@

## [65] rlang_0.4.1             pkgconfig_2.0.2        

>>>>

The manuscript was last compile on 2020-04-29 10:12:35.

@@

\begin{tabular}{llrrrlr}
\toprule
GO ID & Description & Annotated & Significant & Expected & P-value & Adj. p-value\\
\midrule
GO:0003002 & regionalization & 171 & 153 & 133.53 & 0.00012 & 0.123\\
GO:0007224 & smoothened signaling pathway & 75 & 70 & 58.56 & 0.00033 & 0.282\\
GO:0010970 & transport along microtubule & 84 & 77 & 65.59 & 0.00044 & 0.322\\
GO:0006805 & xenobiotic metabolic process & 49 & 47 & 38.26 & 0.00057 & 0.365\\
GO:0048562 & embryonic organ morphogenesis & 154 & 136 & 120.25 & 0.00073 & 0.374\\
\addlinespace
GO:0055114 & oxidation-reduction process & 530 & 457 & 413.85 & 0.00086 & 0.374\\
GO:0060173 & limb development & 90 & 82 & 70.28 & 0.00090 & 0.374\\
GO:0060070 & canonical Wnt signaling pathway & 152 & 134 & 118.69 & 0.00095 & 0.374\\
GO:0006635 & fatty acid beta-oxidation & 38 & 37 & 29.67 & 0.00095 & 0.374\\
GO:0090596 & sensory organ morphogenesis & 138 & 122 & 107.76 & 0.00124 & 0.453\\
\addlinespace
GO:0010811 & positive regulation of cell-substrate ad... & 79 & 72 & 61.69 & 0.00184 & 0.628\\
GO:0060411 & cardiac septum morphogenesis & 33 & 32 & 25.77 & 0.00289 & 0.903\\
GO:0060078 & regulation of postsynaptic membrane pote... & 69 & 63 & 53.88 & 0.00319 & 0.903\\
GO:0042738 & exogenous drug catabolic process & 23 & 23 & 17.96 & 0.00335 & 0.903\\
GO:0021515 & cell differentiation in spinal cord & 23 & 23 & 17.96 & 0.00335 & 0.903\\
\bottomrule
\end{tabular}

@@

## [65] rlang_0.4.5             pkgconfig_2.0.2        
